---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(farsCoursera)
library(maps)
file_list <- list.files(system.file("extdata", package = "farsCoursera"))
from <- lapply(file_list, function(f) {
    file.path(system.file("extdata", package = "farsCoursera"), f)
})
to <- getwd()
lapply(from, function(f) {
    file.copy(f, to)
})
```

# farsCoursera


## Overview

This package allow you to import and summarize data from the
[Fatality Analysis Reporting System](http://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)).
You can also map the locations of accidents on a state map.

## Installation

You can install this package directly from GitHub.

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("JayLKim/farsCoursera")
```

## Usage

** We need to assume that we already have downloaded a data file at the current working directory. **

* Data import (`fars_read_years()`)

If you input a vector of years, you can get a `tibble` of all cases.

```{r "fars_read_years()"}
fars_read_years(c(2013, 2014))
```

* Data summary (`fars_summarize_years()`)

This function summarizes the data you imported. It returns a `tibble`
representing the number of cases per month for a given year.

```{r "fars_summarize_years()"}
fars_summarize_years(c(2013, 2014, 2015))
```

* Accidents map (`fars_map_state()`)

You can map the locations of accidents on a state map. Let's draw an accident
map of Florida in 2013.
(See [this link](https://en.wikipedia.org/wiki/List_of_U.S._state_abbreviations)
for a `state.num`)

```{r "fars_map_state()", fig.height=6, fig.width=6}
fars_map_state(state.num = 12, year = 2013)
```

