---
title: "Playing with the FARS data"
author: "J. Kim"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Playing with the FARS data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
source("./R/fars_functions.R")
```

## Introduction
This package is designed to read data from the
[Fatality Analysis Reporting System](http://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)),
summarize the data, and map the locations of accidents.

## Data Import
Once you have downloaded data files in a current working directory, `fars_read_years()` imports the data into the global environment. To show you
how it works, let's assume that we already have downloaded data file of 2013,
2014, and 2015. You just need to input a vector of years; then, this function
internally generates appropriate file names. So you don't need to be concerned
about a file name.

```{r "fars_read_years()"}
fars_read_years(c(2013, 2014, 2015))
```
