---
title: "Playing with the FARS data"
author: "J. Kim"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Playing with the FARS data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
library(farsCoursera)
library(maps)
file_list <- list.files(system.file("extdata", package = "farsCoursera"))
from <- lapply(file_list, function(f) {
    file.path(system.file("extdata", package = "farsCoursera"), f)
})
to <- getwd()
lapply(from, function(f) {
    file.copy(f, to)
})
```

## Introduction
This package is designed to read data from the
[Fatality Analysis Reporting System](http://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)),
summarize the data, and map the locations of accidents.

## Installation
You can install this package directly from GitHub.

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("JayLKim/farsCoursera")
```

## Data Import
Once you have downloaded data files in a current working directory, `fars_read_years()` imports the data into the global environment. To show you
how it works, let's assume that we already have downloaded data file of 2013,
2014, and 2015. You just need to input a vector of years; then, this function
internally generates appropriate file names. So you don't need to be concerned
about a file name.

```{r "fars_read_years()"}
fars_read_years(c(2013, 2014, 2015))
```

The imported data represent all accident cases per month for a given year.


## Summarizing data
`fars_summarize_years()` helps you summarize the data you imported.

```{r "fars_summarize_years()"}
fars_summarize_years(c(2013, 2014, 2015))
```

As you can see, it returns a `tibble` representing the number of cases per
month for a given year.

## Mapping the locations of accident

`fars_map_state()` draws a map in which every case is represented as a dot.
Let's assume that we want to plot every case occurred at Florida in 2013.

```{r "fars_map_state()", fig.height=6, fig.width=6}
fars_map_state(state.num = 12, year = 2013)
```
